Initial Analysis

### 2020-07-31 Scripts/Initial_Analysis.Rmd
Need to figure out weight method

# Regional UN-sub region area
Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity_id %in% Clean_sau_eez_fes$fishing_entity_id) %>% 
  group_by(sub_region) %>% 
  summarise(Size_Region = sum(Area_km2,na.rm=T)) %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  arrange(sub_region)

@@

SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  filter(!fishing_entity_id %in% c(213,223,207,208)) %>%  # Remove high seas and 207 and 208 that we do not know 
  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
  mutate(value = 1.16 * value)

# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
# SAU_Vicky_Data <- fread(paste(my_path("D"),"Distribution/ReportCatch_FEYrEEZTaxon_2010_14.csv", sep =""))

# Set global values for catch and revenue (within EEZ with re-constructed catch)
SAU_Global_Data <- SAU_Tim_Data %>%
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory) %>% 
  mutate(
    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
    eez_name = gsub("Chile","Chile (mainland)",eez_name),
    eez_name = gsub("Curaçao","Curacao",eez_name),
    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
    eez_name = gsub("Vietnam","Viet Nam",eez_name),
    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
                             ifelse(eez_name == "Greece","Greece (without Crete)",
                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
                                                  ifelse(eez_name == "Italy","Italy (mainland)",
                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
                                                                                     ifelse(eez_name =="Spain (Mediterranean and Gulf of Cadiz)","Spain (mainland, Med and Gulf of Cadiz)",
                                                                                            ifelse(eez_name =="Réunion (France)","Reunion (France)",
                                                                                     eez_name)
                                                                       ))
                                                                       )
                                                         ))))
                             )
                      )
    )))

# List of species
# Spp <- list.files(paste(Results_Path,"Trans_Results/",sep=""))[-829]

# Read Results
# Clean_Results_Trans <- GetTransResults(Spp) %>% 
#   CleanResults(.) %>% 
#   clean_names() %>% 
#   rename(eez_name = territory,
#          fishing_entity = ct_fishing_entity,
#          eez_neighbour = neighbour) %>% 
#   mutate(fishing_entity = ifelse(eez_name == "Spain (Mediterranean and Gulf of Cadiz)","Spain",paste(fishing_entity)))

# Read Results For Carmelia

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
  mutate(
    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
    eez_name = gsub("Chile","Chile (mainland)",eez_name),
    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
    eez_name = gsub("Vietnam","Viet Nam",eez_name),
    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
                             ifelse(eez_name == "Greece","Greece (without Crete)",
                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
                                                  ifelse(eez_name == "Italy","Italy (mainland)",
                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
                                                                                     eez_name)
                                                                       ))
                                                         ))))
                             )
                      )
    )

Clean_Results_Trans %>% anti_join(Clean_sau_eez_fes, by = "eez_name") %>% 
  group_by(eez_name) %>% 
  summarise(n())

@@

@@

# Get the total values for the world excluding not identified species
Total_SAU_id <- SAU_Global_Data %>% 
  left_join(Exploited_Species) %>% # list of SAU exploited species identified
  filter(!is.na(taxon_name)) %>% # reove those NAs 
  group_by(Variable) %>% 
  summarize(Total_id = sum(Value,na.rm=T),
            id_nspp = length(unique(taxon_key))
            )

@@

# Percentage catch of species analyzed from the identified species
Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.52%

# Percentage species analyzed from the identified species
Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.22%

# When we do not remove the groups that are not species level the number sampled drops to ~60%

### So what species are NOT there? 
#  Absten species
# Missing_Species <- SAU_Global_Data %>%
#   filter(!taxon_key %in% Species_Sampled$TaxonKey) %>% 
#   left_join(Exploited_Species) %>% 
#   filter(!is.na(taxon_name)) %>% 
#   group_by(taxon_key,taxon_name,common_name) %>% 
#   summarise(sum(Value))

@@

# Filter SAU data for only those sampled species
SAU_Sampled_Data <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
  left_join(Exploited_Species) %>% 
  filter(!is.na(taxon_name)) %>% 
  clean_names() %>% 
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

# Numbers for paper
Summary_Trans <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Sampled_Data) %>% 
  filter(taxon_key %in% Species_Sampled$TaxonKey) %>%
  semi_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")
  ) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

@@

# Average data for the last 10 years

SAU_Global_Vicky <- SAU_Vicky_Data %>% 
  filter(#eezid != 0,
         year == 2006) %>%
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise_at(c("sumcatch"),
               mean,na.rm=T)

## Get the total of global data
Total_SAU_Vicky <- sum(SAU_Global_Vicky$sumcatch,na.rm = T)

Summary_Trans_vicky <- Tresholded_T_Data %>% 
  select(taxon_key,eez_name) %>% 
  group_by(taxon_key,eez_name) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  select(-n) %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>% 
  group_by(taxon_key,fishing_entity_id) %>% 
  summarise(n()) %>% 
  left_join(SAU_Global_Vicky,
            by = c("taxon_key","fishing_entity_id")) %>% 
  # filter(eezid != 0) %>% # I think they used high seas data as well?
  group_by() %>%
  summarise(Total_Trans = sum(sumcatch, na.rm=T)) %>% 
  mutate(Per_sampled = Total_Trans/Total_SAU_Vicky*100); Summary_Trans_vicky

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
    area_index > Max_AI |
    model_index < MI
  ) %>% 
  group_by(taxon_key,fishing_entity,eez_name) %>% 
  summarise(n()) %>% 
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity"))

@@

Summary_Discrete <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Sampled_Data) %>% 
  semi_join(Discrete,
            by = c("taxon_key","fishing_entity")
            ) %>% # only counting the catch from transboundary speices (e.g. anchoveta from chile and peru but not from equador)
  group_by(Variable) %>%
  summarise(Total_Dis = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Dis/Total_Sampled*100,
         Per_SAU = Total_Dis/Total_Global*100)

###_________________###
# Discrete Exclusive
# Species that are only discrete and are not present in the transboundary category
###_________________###

@@

Summary_Discrete_Exclusive <- Discrete_Exclusive %>% 
  left_join(SAU_Sampled_Data) %>% 
  group_by(Variable) %>%
  summarise(Total_Discrete = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Discrete/Total_Sampled*100,
         Per_SAU = Total_Discrete/Total_Global*100)

@@

Determine the number of species per territory

@@

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_id) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  # left_join(EEZ_Area, 
  #           by = "eez_name") %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    # Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    # Weight_Bins = cut(Weight_Spp,breaks = 5),
    # Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           # labels = c('super low', 'low','median', 'high','super high')
    # )
  )

@@

Total_Value_EEZ <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(SAU_Global_Data) %>% 
  group_by(fishing_entity,Variable) %>% 
  summarise(Total_Value = sum(Value,na.rm=T))

Value_Trans_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = c("fishing_entity","fishing_entity_id")
            ) %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  # left_join(Entity_Area,
  #           by = "fishing_entity") %>%
  # # Include the weighted method for supplementals
  # mutate_at(
  #   vars(catch,value),
  #   funs(weight= ./(Size_Entity/1000000))
  # ) %>%
  # gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
  gather("Variable","Value",catch:value) %>%
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

@@

# Continental level for transboundary species
Continent_Trans_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(georegion = ifelse(is.na(georegion), "Other",paste(georegion))) %>% 
  group_by(georegion,Variable) %>% 
  summarise_if(is.numeric,sum,na.rm=T) #%>% 
  # select(-Size_Entity,-Trans_Entity_n)

@@

Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region,Variable) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T) %>%
  # select(-Size_Entity,-Trans_Entity_n) %>% 
  arrange(Variable) %>%
  ungroup() %>% 
  mutate(id = rep(seq(1,17),2)) %>% 
  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))

@@

Produce the map of transboundary species within each EEZ and the value in catch/revenue within each country

@@

```{r Weight_Revenue, eval =F, echo =F}

@@

# Total revenue from Top countries
Total_Top_Rev <- Value_Trans_Country %>% 
  filter(Variable == "value") %>% 
  filter(fishing_entity %in% Top_Rev_Countries) %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  left_join(Subregion_Trans_raw_Value) %>% 
  mutate(Per_Top = Value/Value_sum*100) %>% 
  select(1:3,Per_Top)

Top_Rev <- sau_eez_fes %>% 
  filter(fishing_entity %in% Top_Rev_Countries) %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  filter(Variable == "value") %>% 
  left_join(Exploited_Species) %>% 
  group_by(fishing_entity) %>%
  top_n(16,Value) %>%
  select(fishing_entity,Variable,Value,taxon_name) %>% 
  mutate(Top_Value = Value/1000000) %>% # Million of USD
  select(-Value) %>% 
  left_join(Total_Top_Rev,
            by = c("fishing_entity","Variable")
            ) %>% 
  mutate(Ratio = Top_Value/Value*100)

Top_Rev %>% 
  group_by(fishing_entity) %>% 
  summarise(sum(Ratio))

### Total revenue from the top 5

@@

@@

>>>>

Entity_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_Results_Trans,
            by = "eez_name") %>% 
  group_by(fishing_entity) %>% 
  summarise(Size_Entity = sum(Area_km2))

# Regional UN-sub region area
Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity_id %in% Clean_sau_eez_fes$fishing_entity_id) %>% 
  select(-geometry) %>% 
  group_by(sub_region) %>% 
  summarise(Size_Region = sum(Area_km2,na.rm=T)) %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  arrange(sub_region)

@@

SAU_Global_Data <-fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>%
  # Remove high seas and 207 and 208 that are unknown
  filter(!fishing_entity_id %in% c(213,223)) %>%  # 207,208
  # Allocate catch of islands to UK
  mutate(fishing_entity_id = ifelse(fishing_entity_id %in% c(219,220), 183,fishing_entity_id)) %>% 
  # Convert to 2019 real USD
  mutate(value = 1.16 * value) %>%
  # Average 10 years of data
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory) %>% 
  mutate(
    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
    eez_name = gsub("Chile","Chile (mainland)",eez_name),
    eez_name = gsub("Curaçao","Curacao",eez_name),
    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
    eez_name = gsub("Vietnam","Viet Nam",eez_name),
    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
                             ifelse(eez_name == "Greece","Greece (without Crete)",
                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
                                                  ifelse(eez_name == "Italy","Italy (mainland)",
                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
                                                                                     ifelse(eez_name =="Spain (Mediterranean and Gulf of Cadiz)","Spain (mainland, Med and Gulf of Cadiz)",
                                                                                            ifelse(eez_name =="Réunion (France)","Reunion (France)",
                                                                                                   eez_name)
                                                                                     )
                                                                              )
                                                                       )
                                                                )
                                                         )
                                                  )
                                           )
                                    )
                             )
                      )
    )
  )

# Load Transboundary Results

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
  mutate(
    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
    eez_name = gsub("Chile","Chile (mainland)",eez_name),
    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
    eez_name = gsub("Vietnam","Viet Nam",eez_name),
    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
                             ifelse(eez_name == "Greece","Greece (without Crete)",
                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
                                                  ifelse(eez_name == "Italy","Italy (mainland)",
                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
                                                                                     eez_name)
                                                                       )
                                                                )
                                                         )
                                                  )
                                           )
                                    )
                             )
                      )
    )
    )

@@

### Transboundary Species

@@

# Get the total values for the world excluding not identified species
Total_SAU_id <- SAU_Global_Data %>% 
  filter(taxon_key %in% Exploited_Species$taxon_key) %>%
  group_by(Variable) %>% 
  summarize(Total_id = sum(Value,na.rm=T),
            id_nspp = length(unique(taxon_key))
  )

@@

# Percentage catch of species analyzed from the identified species
Total_Catch_Spp <- Total_SAU_Sampled$Total_Sampled[1]/Total_SAU_id$Total_id[1] *100 #96.49%

# Percentage species analyzed from the identified species
Total_spp_analyzed <-Total_SAU_Sampled$Sampled_nspp[1]/Total_SAU_id$id_nspp[1]*100 #63.23%

@@

# Filter SAU data for only those sampled species
SAU_Sampled_Data <- SAU_Global_Data %>% 
  filter(taxon_key %in% Exploited_Species$taxon_key)

# Numbers for paper

Summary_Trans <- SAU_Sampled_Data %>% 
  semi_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity_id")
  ) %>% 
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

### Discussion with Teh

@@

# Read SAU non-reconstructed catch data from 2006 for comparrisonwith Sumaila
# Provided by Vicky Lam
SAU_FAO_Data <- fread(paste(my_path("D"),"Distribution/LVCatch_byYrEEZFETaxa_2005_09.csv", sep ="")) %>% 
  filter(#eezid != 0,
         year == 2006) %>%
  group_by(fishing_entity_id,taxon_key,eezid) %>% 
  summarise_at(c("sumcatch"),
               sum,na.rm=T)

## Get the total of global data
Total_SAU_FAO <- sum(SAU_FAO_Data$sumcatch,na.rm = T)

# Estimate numbers for paper
SAU_FAO_Data %>% 
  semi_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity_id")
  ) %>% 
  group_by() %>% 
  summarise(Total_Trans = sum(sumcatch, na.rm=T)) %>% 
  mutate(Per_Sau_FAO = Total_Trans/Total_SAU_FAO*100)

### Discrete Species

Based on our assessment (see Methods), 590 transboundary species were also identified as "discrete" species, meaning that the same species could be shared by two neighboring EEZs (transboundary) but not with a third neighbor (discrete).

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
    area_index > Max_AI |
    model_index < MI
  ) %>% 
  group_by(taxon_key,fishing_entity,eez_name) %>% 
  summarise(n()) %>% 
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")) %>% 
  left_join(Clean_sau_eez_fes)

@@

Summary_Discrete <- SAU_Sampled_Data %>% 
  semi_join(Discrete,
            by = c("taxon_key","fishing_entity_id")
  ) %>% 
  group_by(Variable) %>%
  summarise(Total_Trans = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Trans/Total_Sampled*100,
         Per_SAU = Total_Trans/Total_Global*100)

### Discrete Exclusive

Within these species, 305 were considered exclusively discrete, that is, they could be fished by neighboring nations but were not considered transboundary according to our methods of determination (See methods).

```{r Discrete_Exclusive_per_Territory, eval = F, echo = F}
###_________________###
# Discrete Exclusive
# Species that are only discrete and are not present in the transboundary category
###_________________###

@@

# Numbers for paper
Summary_Discrete_Exclusive <- Discrete_Exclusive %>% 
  left_join(SAU_Sampled_Data) %>% 
  group_by(Variable) %>%
  summarise(Total_Discrete = sum(Value, na.rm=T)) %>% 
  left_join(Total_SAU_Sampled) %>% 
  left_join(Total_SAU_Global) %>% 
  mutate(Per_sampled = Total_Discrete/Total_Sampled*100,
         Per_SAU = Total_Discrete/Total_Global*100)

@@

### Data For Map

We group countries according to the United Nations sub-regions and found that transboundary species are particularly economically important for Northern America and Eastern Asia

@@

EEZ_Area <- World_sf %>% 
  as.data.frame() %>% 
  group_by(eez_id) %>% 
  summarise(Size_EEZ = sum(Area_km2))

Entity_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_Results_Trans,
            by = "eez_name") %>% 
  group_by(fishing_entity) %>% 
  summarise(Size_Entity = sum(Area_km2))

# Data per Territory (EEZ)
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_id) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area,
            by = "eez_id") %>%
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                           labels = c('super low', 'low','median', 'high','super high')
    )
  )

@@

Total_Value_EEZ <- Clean_sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(SAU_Global_Data) %>% 
  group_by(fishing_entity,Variable) %>% 
  summarise(Total_Value = sum(Value,na.rm=T))

Value_Trans_Country <- Clean_sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  left_join(Tresholded_T_Data,
            by = c("fishing_entity","fishing_entity_id")
            ) %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand
                                Trans_Total)
                         )
  ) %>% 
  spread(Variable,Trans_Total) %>% 
  left_join(Entity_Area,
            by = "fishing_entity") %>%
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./(Size_Entity/1000000))
  ) %>%
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>%
  # gather("Variable","Value",catch:value) %>%
  group_by(fishing_entity,Variable,Value) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_EEZ,
            by = c("fishing_entity", "Variable") 
            ) %>% # uncomment for estimating percentage
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                         Value),
    Trans_Per = (Value/Total_Value)*100000000 #Return to percentage
  )

### Data for continental analysis

@@

# Continental level for transboundary species
Continent_Trans_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(georegion = ifelse(is.na(georegion), "Other",paste(georegion))) %>% 
  group_by(georegion,Variable) %>% 
  summarise_if(is.numeric,sum,na.rm=T)

@@

Subregion_Trans_raw_Value <- Value_Trans_Country %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region,Variable) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T) %>%
  arrange(Variable) %>%
  ungroup() %>% 
  mutate(id = rep(seq(1,17),2)) %>% 
  mutate(Value_sum=ifelse(Variable == "catch" & Value_sum >= 12,12,Value_sum))

@@

Figure 1. Number of transboundary species and their contribution to global fisheries catches and revenue. A) The number of species and amount of revenue are represented by color coding of EEZs and land polygons, respectively. B) Contribution of transboundary species to regional revenue (left) and catch (right). Regions according to the United Nations sub-regions. Points = mean +- sd. Revenue in 2010 real USD

@@

# Total revenue from Top countries
Total_Top_Rev <- Value_Trans_Country %>% 
  # filter(Variable == "value") %>% 
  filter(fishing_entity %in% Top_Rev_Countries) %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  left_join(Subregion_Trans_raw_Value) %>% 
  mutate(Per_Top = Value/Value_sum*100) %>% 
  select(1:3,Per_Top)

### Percentaga that top 5 represents

## Weighted bar plots

### Data for Weighted plot
```{r Weight_Revenue, eval =F, echo =F}
r
Continent_Trans_Value <- Subregion_Trans_raw_Value %>% 
  left_join(Regional_Area,
            by = "sub_region") %>% 
  mutate(
    Value_sum= Value_sum*1000000,
    weighted_value = Value_sum/Size_Region
    )

@@

@@

*We determined the exploitation category of each species according to the catch trend within each EEZ (Fig. 3).

### Data for Circular plot

@@

### Circular plot
